\documentclass[]{article}

%opening
\title{Review report of meeting Monday the 17th of March 2014}

\begin{document}

\maketitle


\section*{Participants}
\begin{itemize}
\item \textbf{Group 5} - Jesper Bj\o rnholt, Jonas Bredvig Bendix Nielsen, Jonas Elb\ae kgaard J\o rgensen, Mads Engesgaard Jacobsen, Rasmus Lomholt Wismann \& Tom M\o rk Christensen.
\item \textbf{Group 6} - Asbj\o rn Fjelbro Steffensen, Jacob Benjamin Cholewa, Jakob Merrild, Mathias Kindholm Pedersen, Nicki Hjorth J\o rgensen \& Thomas Stoy Dragsb\ae k
\end{itemize}
\section*{What was reviewed}
Initial draft of the report that group 5 is working on for the course System Development and Project Organisation(BSUP). This included an introduction, a problem statement and a description of the methods the group intended to deploy in order to answer the problem statement.
\section*{What was approved}
\begin{itemize}
\item Overall well formulated report.
\item The use of third person when writing about the group performing the project they examine helps clarifying that it is a separate project.
\end{itemize}
\section*{What was not approved}
\begin{itemize}
\item \textbf{Introduction}
	\begin{itemize}
	\item Grammatical error in second paragraph of the introduction where both past and present tense was used.
	\end{itemize}

\item \textbf{Problem statement}
	\begin{itemize}
	\item It might be unrealistic to expect to be given the data which was described as being expected.
	\item It will be difficult to register the actual amount of time used on the project.
	\item It is not possible to compare actual and estimated time consumption unless the estimate is made with a unit of time.
	\item Missing a reflective part.
	\item It is not well defined what structured and effective entails.
	\end{itemize}
\item \textbf{Description of method}
	\begin{itemize}
	\item The method described for answering the question "How did the estimate effect the planning?" is a circular argument.
	\item It is unclear how the questionnaires will help answer the question of how effective and well structured the project was.
	\end{itemize}
\end{itemize}

\section*{Follow-up plan}
Group 5 takes the received feedback into account and at the next review meeting there will be a follow-up on whether these criteria have been met: 
\begin{itemize}
\item Grammatical errors have been corrected in the introduction
\item The problem statement includes a reflective part
\item The method for answering the question "How did the estimate effect the planning?" is no longer a circular argument
\end{itemize}
\end{document}
